---
title: "Airport Coordinates"
author: "Rodrigo Suzuki Okada"
date: "2/13/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Dataset

This web presentation features a map of airports around the world, created with Leaflet in R.

```{r, echo=FALSE, eval=TRUE}
library(leaflet)
```

The dataset itself is available [here](http://www.chocolatesoftware.com/forum/index.php?topic=839.0). It consists of a list of airports by ICAO code, latitude, longitude and altitude (in feet).

```{r, echo=TRUE, eval=TRUE}
airports <- read.csv("icao_airports.csv", 
                     col.names = c("code", "lat", "lng", "alt"))
head(airports)
```

## Preparing the map

Each marker on the map will be presented with a airplane icon. The [original file](https://commons.wikimedia.org/wiki/Category:Aircraft_icons)
is available on Wikimedia Commons.

```{r, echo=TRUE, eval=TRUE}
airplaneIcon <- makeIcon(iconUrl = "airplane_icon.png", 
                         iconWidth = 32, iconHeight = 32, 
                         iconAnchorX = 16, iconAnchorY = 16)
```

The markers will have popup information with the airport's code and coordinates.

```{r, echo=TRUE, eval=TRUE}
airports$legend <- paste(airports$code, 
                         paste("lat", airports$lat, sep = " "), 
                         paste("lng", airports$lng, sep = " "), 
                         sep = "<br/>")
```

***

```{r, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
leaflet(airports) %>%
    addTiles() %>%
    addMarkers(clusterOptions = markerClusterOptions(), 
               icon = airplaneIcon,
               popup = airports$legend)
```
